---
name: "Jacob"
surname: "Ellison"
position: "Data Analyst | Publishing Professional"
address: "200 Waverly Place, Apt. 21, New York, NY 10014"
phone: 607 346 5403
email: "jakesellison@gmail.com"
github: "jakesellison"
linkedin: "jacob-ellison-0b7b26105"
date: "`r format(Sys.time(), '%B %Y')`"
headcolor: 414141
output: vitae::awesomecv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(vitae)
library(tinytex)
library(tibble)
```

# Experience

```{r}
tribble(
  ~ Company, ~ Duration, ~ Position, ~ Location, ~ Details,
    #KAPLAN Strategy
  "Kaplan North America", "June. 2021 - Present", "Senior Strategic Analyst", "New York, NY", 
  c("Analyze Kaplan's strategies on Amazon, including advertising, merchandising, inventory
management, and customer engagement, and identify other opportunities and risks throughout the retail publishing landscape",
    "Work cross-functionally between Publishing and Data Engineering to provide subject-matter expertise on data ingestion and warehousing",
"Develop dashboards in R Shiny (with ggplot visualizations) hosted on R Studio Connect. Projects include developing tools to execute on operational necessities as well as macro-level data visualizations to guide strategic initiatives"),
  #KAPLAN Ops
  "Kaplan North America", "Mar. 2020 - Present", "Operations Analyst", "New York, NY", 
  c("Created and continuously improved R scripts to format, present, and analyze large sales and inventory datasets",
    "Aggregated data sources from many several different businesses and sales channels to provide a comprehensive view of Kaplan's publishing business",
    "Forecasted sales patterns and inventory requirements to execute reprint decisions"),
  #ABRAMS
  "Abrams", "Feb. 2019 - Mar. 2020", "Sales Assistant", "New York, NY",
  c("Interpreted and manipulated sales data from multiple reporting portals to guide operational sales decisions",
    "Identified efficient solutions to automate routine deliverables (assembling title metadata, sales numbers, and inventory performance) which were previously assembled manually"),
  #MEETUP
  "Meetup", "Sep. 2018 - Dec. 2018", "Community Support Specialist", "New York, NY",
  c("Composed solution-oriented responses to customers while troubleshooting product challenges with the Meetup website",
    "Collaborated with other support specialists to develop and document best practices on Confluence"),
) %>% 
  detailed_entries(Company, Duration, Position, Location, Details)
```

# Education

```{r}
tribble(
  ~ Degree, ~ Year, ~ Institution, ~ Where, ~ Coursework,
  "MS, Publishing: Digital and Print Media", "Aug. 2018 - May 2020", "New York University", "New York, NY",
  c("Statistical Measurements, Analysis, and Research with Jeffrey Baliban: Framed marketing decisions with
  statistical tools and built a foundation in data ethics, data cleaning, and data analysis"),
  "BA, Major: Russian and Eurasian Studies // Minor: Computer Science", "Aug. 2011 - May 2015", "Colgate University", "Hamilton, NY", c()
) %>% 
  detailed_entries(Degree, Year, Institution, Where, Coursework)
```

# Languages and Skills

```{r}
tribble(
  ~ Item, ~ Level, ~ Desc,
  "R", 'Expert', c(
    "Dashboard design in R Shiny to measure KPIs and increase data transparency",
    "ETL with custom R scripts to ingest data and push updates to a MySQL database",
    "Reporting automation with R Markdown documents published to R Studio Connect",
    "Custom email-distributed reports facilitated by the Gmail API and Rstudio Connect"),
  "SQL", 'Intermediate', c("Queries to obtain data from Amazon Redshift and MySQL databases","Building views to consolidate data and deliver common queries to stakeholders", "Optimization using SQL EXPLAIN to identify coding inefficiencies"),
  "Tableau", "Intermediate", c("Creating and publishing visualizations", "Utilizing custom joins and calculations")
) %>% 
  detailed_entries(
    with = Item,
    what = Level,
    why = Desc
  )
